---
title: 'Project'
author: "Yixin Lian yl4089"
date: "2018/**/**"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

My goal is to focus on the time variable in our dataset. Our dataset includes an even sample of the customer reviews for electronic products sold on Amazon and BestBuy websites. 
```{r}
library(tidyverse)
library(lubridate)
library(plotly)
#electron_data <- 
#  read.csv(file="/Users/easonlian/Desktop/programming/eda/Project/DatafinitiElectronicsProductData.csv", 
#                            header=TRUE, sep=",")

electron_data <- 
  read.csv(file="../data/DatafinitiElectronicsProductData.csv", 
                            header=TRUE, sep=",")

```


First we take a look at the NA value of our dataset. It shows there are only four variabls have na values. The dataset is relatively complete. 

```{r}
colSums(is.na(electron_data))
```

Then we select the key variables we would like to investigate. 

```{r}
yx_select <- select(electron_data, name, brand, reviews.date, reviews.rating)
yx_select <- yx_select[rowSums(is.na(yx_select)) == 0, ] #remove na rows
yx_select$reviews.date <- as.Date(yx_select$reviews.date)
library(ggplot2)

library(tidyverse)
head(yx_select)
#yx_select$name <- abbreviate(yx_select$name, minlength = 2)
```



```{r}
library(shiny)
library(DT)
library(dplyr)
#runExample("01_hello")
product_name <- unique(yx_select$name)
brand_name <- unique(electron_data$brand)

average_rating_select <- yx_select %>% group_by(name, month = floor_date(reviews.date, unit = "month")) %>% summarise(average.rating = mean(reviews.rating, na.rm=TRUE))

average_rating_select2 <- yx_select %>% group_by(brand, month = floor_date(reviews.date, unit = "month")) %>% summarise(average.rating = mean(reviews.rating, na.rm=TRUE))

```


```{r}
#sentiment score analysis for brand
library(reshape2)
library(sentimentr)
library(plotly)
sen_text <- get_sentences(as.character(electron_data$reviews.text))
sen_text <- sentiment_by(sen_text)

electron_data_with_sentiment <- electron_data
electron_data_with_sentiment['sentiment.score'] <- sen_text$ave_sentiment

summarise_table_0 <- electron_data_with_sentiment %>% 
  select(brand, reviews.doRecommend, reviews.rating, sentiment.score)%>% 
  na.omit() %>%
  group_by(brand) %>% 
  summarise(n = n(), average.rating = sum(reviews.rating)/n(), average.sentiment = sum(sentiment.score)/n(),    prop.recommend = sum(reviews.doRecommend)/n())

sentiment_plot_brand <- plot_ly(summarise_table_0, x = ~average.rating, y = ~average.sentiment, z = ~prop.recommend, size=4, text=~paste('Rating:',round(average.rating, 3),'<br>Sentiment:',round(average.sentiment, 3), '<br>Recommend:', round(prop.recommend, 3), '<br>Brand:', brand)) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'Rating'),
                     yaxis = list(title = 'Sentiment'),
                     zaxis = list(title = 'Do Recommend')))

#sentiment score analysis for product
summarise_table_0 <- electron_data_with_sentiment %>% 
  select(name, reviews.doRecommend, reviews.rating, sentiment.score)%>% 
  na.omit() %>%
  group_by(name) %>% 
  summarise(n = n(), average.rating = sum(reviews.rating)/n(), average.sentiment = sum(sentiment.score)/n(),    prop.recommend = sum(reviews.doRecommend)/n())

sentiment_plot_product <- plot_ly(summarise_table_0, x = ~average.rating, y = ~average.sentiment, z = ~prop.recommend,size=4, text=~paste('Rating:',round(average.rating, 3),'<br>Sentiment:',round(average.sentiment, 3), '<br>Recommend:', round(prop.recommend, 3), '<br>name:', substr(name, 1, 30))) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'Rating'),
                     yaxis = list(title = 'Sentiment'),
                     zaxis = list(title = 'Do Recommend')))
```

```{r}
#two y axis plot product
my_text = get_sentences(as.character(electron_data$reviews.text))
sen_text = sentiment_by(my_text)

electron_data$reviews.date <- as.Date(electron_data$reviews.date)


sentiment_df = data.frame(electron_data$name, electron_data$reviews.date,sen_text$ave_sentiment, electron_data$reviews.rating)

colnames(sentiment_df)[1]<-"name"
colnames(sentiment_df)[2]<-"review_date"
colnames(sentiment_df)[3]<-"text_scores"
colnames(sentiment_df)[4]<-"rating"

sentiment_df <- sentiment_df[rowSums(is.na(sentiment_df)) == 0, ] #remove na rows

#two y axis plot brand
sentiment_df_brand = data.frame(electron_data$brand, electron_data$reviews.date,sen_text$ave_sentiment, electron_data$reviews.rating)

colnames(sentiment_df_brand)[1]<-"brand"
colnames(sentiment_df_brand)[2]<-"review_date"
colnames(sentiment_df_brand)[3]<-"text_scores"
colnames(sentiment_df_brand)[4]<-"rating"

sentiment_df_brand <- sentiment_df_brand[rowSums(is.na(sentiment_df_brand)) == 0, ] #remove na rows
```

```{r}
amazon_electronics_do_recommend <- electron_data[electron_data$reviews.doRecommend == TRUE, ]
amazon_electronics_donot_recommend <- electron_data[electron_data$reviews.doRecommend == FALSE, ]

stop_words <- c("i", "me", "my", "myself", "we", "our", "ours", "ourselves", "you", "your", "yours", "yourself", 
                "yourselves", "he", "him", "his", "himself", "she", "her", "hers", "herself", "it", "its", "itself", 
                "they", "them", "their", "theirs", "themselves", "what", "which", "who", "whom", "this", "that", "these", 
                "those", "am", "is", "are", "was", "were", "be", "been", "being", "have", "has", "had", "having", "do", 
                "does", "did", "doing", "a", "an", "the", "and", "but", "if", "or", "because", "as", "until", "while", 
                "of", "at", "by", "for", "with", "about", "against", "between", "into", "through", "during", "before", 
                "after", "above", "below", "to", "from", "up", "down", "in", "out", "on", "off", "over", "under", "again", 
                "further", "then", "once", "here", "there", "when", "where", "why", "how", "all", "any", "both", "each", 
                "few", "more", "most", "other", "some", "such", "no", "nor", "not", "only", "own", "same", "so", "than",
                "too", "very", "s", "t", "can", "will", "just", "don", "should", "now")

```

```{r}
# Define UI for application that draws a histogram
ui <- shinyUI(fluidPage(

  # Application title
  titlePanel("Amazon Electronic Product Data Analysis"),
  
  navbarPage(
  "Menu", 
  tabPanel("Overview", 
     p("Our analysis revolves around a dataset containing 7,000 online reviews for electronic products sold in Amazon, Walmart, BestBuy and other online platforms provided by ",span("Datafiniti's Product Database", style = "color:blue"),". Furthermore, the reviews cover 50 different electronic products under 38 different brands."),
     p("The challenge we face is to address a series of product-related key questions that helps explain how customer feedback could influence electronic product buying process via interactive visualization:"),
     em("1. What are the trends for these electronic products?"),br(),
     em("2. What is the correlation between ratings and reviews?"),br(),
     em("3. How is online reputation of different brands?"),br(),
     em("4. What is shared/different pattern of ratings among brands?"),br(),br(),
     p("A brief walkthrough of this app's sections is as following:"),
     h4("Tab: Product"),p(strong("SelectInput widget: "), "allows user can examine a specific product."),
     p(strong("General tab: "),"display (i) average rating of selected product given by users during different
                               months; (ii) perentage of users who vote recommend, not recommend or NA; 
                               (iii) distribution of 1-5 star ratings given by all users."),
     p(strong("User Review Highlight tab: "), "designed to give buyers some insight from other customers' review. Buyers can view product users' sentiment score and number of reviews over time; a word cloud that displays key words from these reviews; and top 10 reiews that other users think are most helpful."),
     h4("Tab: Brand"), p(strong("SelectInput widget: "), "allows user can examine a specific brand."),
     p(strong("General tab: "),"display (i) average rating of selected brand given by users during different
                               months; (ii) perentage of users who vote recommend, not recommend or NA; 
                               (iii) distribution of 1-5 star ratings given by all users."),
     p(strong("User Review Highlight tab: "), "designed to give buyers some insight from other customers' review of a certain brand. Buyers can view product users' sentiment score and number of reviews over time; a word cloud that displays key words from these reviews; and top 10 reiews that other users think are most helpful."),
     h4("Tab: Comparison"), p("Two 3-D plots displaying online image across all 35 brands and 50 products. The plot reveals information from 3 different angles: Rating, review sentiment score and percentage recommend. User can compare products or brands acccording to their relative position in the 3-d space. This also reveals what aspect the product/brand performs least satifiably so that it can draw more attention during product development."),
     h4("Tab: Data"), p("Display raw data if users want to look up a specfic review.")
           ),
  tabPanel("Product",
  sidebarLayout(
    sidebarPanel(
      width = 3,
      #textInput("title", "Plot title:", value = "x v y"),
      fluidRow(selectInput("select_product", "Select a Product:", choices = product_name, selected = "Microsoft Surface Pro 4 Type Cover with Fingerprint ID"),
               div(style = "height:0px;"))
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
      tabsetPanel(
        id = "inTabset",
        tabPanel(title = "General", value = "panel1", 
          fluidRow(h3("Genenral Overview for Selected Product"),
            h4("Popularity Over Time"),
            plotlyOutput(outputId = "product_plot")),
      
          fluidRow(
            class = "myRow2",
            div(style = "margin-top:2em"),
            column(width = 6, h4("User DoRecommend"), plotOutput(outputId = "pie")), 
            column(width = 6, h4("Rating Distribution"), plotOutput(outputId = "bar"))
          )
        ),
        tabPanel(title = "User Review Text Highlight", value = "panel2", 
                 fluidRow(plotOutput(outputId = "product_review_analysis")),
                 fluidRow(plotOutput(outputId = "product_wordcloud")),
                 fluidRow(dataTableOutput('product_helpful_comments'))
                 )
      )
    )
  )),
  tabPanel("Brand",
    sidebarLayout(
      sidebarPanel(
        width = 3,
        fluidRow(selectInput("select_brand", "Select a Brand:", choices = brand_name, selected = "Microsoft"),
                 div(style = "height:0px;"))
      ),
      
      mainPanel(
      tabsetPanel(
        id = "inTabset2",
        tabPanel(title = "General", value = "brand_panel1", 
          fluidRow(h3("Genenral Overview for Selected Brand"),
            h4("Popularity Over Time"),
            plotlyOutput(outputId = "brand_plot")),
      
          fluidRow(
            div(style = "margin-top:2em"),
            column(width = 6, h4("User DoRecommend"), plotOutput(outputId = "pie2")), 
            column(width = 6, h4("Rating Distribution"), plotOutput(outputId = "bar2"))
          )
        ),
        tabPanel(title = "User Review Text Highlight", value = "brand_panel2", plotOutput(outputId = "brand_review_analysis"))
      )
      )
    )  
  ),
  tabPanel("Comparison",
    fluidRow(column(width = 12, 
      h3("Comparison by Product"),
      plotlyOutput(outputId = "product_comparison"),
      h3("Comparison by Brand"),
      plotlyOutput(outputId = "brand_comparison")
      
    ))
  ),
  tabPanel("Data",
    DT::dataTableOutput("data_table")
    #hover = hoverOpts(id ="plot_hover"),
    #uiOutput("my_tooltip"))
  ))
  
  )
)
#------------------------------------------------------------------------------#
##server script
#------------------------------------------------------------------------------#
server <- shinyServer(function(input, output) {
  

#------------------------------------------------------------------------------#
##product page 
#------------------------------------------------------------------------------#
  output$product_plot <- renderPlotly({
    
      selected = average_rating_select[average_rating_select$name == input$select_product,]
  
      p <- ggplot(selected,
             aes(x=month, y=average.rating)) +
        geom_line() + stat_smooth() + xlab("Month") + ylab("Average Rating")
      
      ggplotly(p, height = 400)
    
    
  })
  
  output$product_review_analysis <- renderPlot({
    
      product = sentiment_df[sentiment_df$name == input$select_product,]
      tidy_table <- product %>% group_by(month = floor_date(review_date, unit = "month")) %>% summarise(ave_review_text_scores = sum(text_scores)/n(), ave_rating = sum(rating)/n())
      tidy_table = data.frame(tidy_table)
      p <- ggplot(tidy_table, aes(x = month))
      p <- p + geom_line(aes(y = ave_review_text_scores, colour = "Sentimental Scores"))
      p <- p + geom_line(aes(y = ave_rating/13, colour = "Ave_rating")) 
      p <- p + scale_y_continuous(sec.axis = sec_axis(~.*13, name = "Average Rate stars"))
      p <- p + scale_colour_manual(values = c("blue", "red"))
      p <- p + labs(y = "Sentimental Scores",
                    x = "Month",
                    colour = "Parameter")
      p <- p + theme(legend.position = c(0.8, 0.9))
      p
  })
  
  output$product_wordcloud <- renderPlot({
      amazon_electronics_do_recommend_product <- amazon_electronics_do_recommend[amazon_electronics_do_recommend$name == input$select_product, ]
      corpus_review <- Corpus(VectorSource(amazon_electronics_do_recommend_product$reviews.text))
#View(corpus_review)
      corpus_review <- tm_map(tm_map(tm_map(corpus_review, tolower), removePunctuation), removeWords, stop_words)

      review_dtm <- DocumentTermMatrix(corpus_review)
      review_tdm <- TermDocumentMatrix(corpus_review)
      review_m <- as.matrix(review_tdm)
      review_term_freq <- rowSums(review_m)
      review_term_freq <- sort(review_term_freq, decreasing = T)
      review_word_freq <- data.frame(term = names(review_term_freq),
                               num = review_term_freq)
      wordcloud(review_word_freq$term, review_word_freq$num,
                max.words = 30, colors = c("blue","darkgoldenrod","tomato"))
  })
  
  output$product_helpful_comments<- renderDataTable(
    electron_data[electron_data$name == input$select_product, c("reviews.text", "reviews.numHelpful")] %>% arrange(desc(reviews.numHelpful)) %>% top_n(9)
  )
    
  output$pie <- renderPlot({
    
      product_recommend <- electron_data[electron_data$name == input$select_product, 'reviews.doRecommend']
      product_recommend[is.na(product_recommend)] <- "NA"
      product_recommend <- data.frame(product_recommend)
      par(mar=c(0,0,0,0))
      #pie(table(product_recommend, exclude = NULL), col = c("pink", "grey", "light green"))
      p <- ggplot(product_recommend, aes(x='', fill=product_recommend)) +
      geom_bar(width = 1, stat = "count") +
      coord_polar(theta = "y", start = 0) + theme(legend.position="top",axis.title=element_blank(),axis.ticks = element_blank())
      p 
    
  })
  
  output$bar <- renderPlot({
      par(mar=c(0,0,0,0))
      product_rating <- electron_data[electron_data$name == input$select_product, 'reviews.rating']
      product_rating <- product_rating[!is.na(product_rating)]
      product_rating <- data.frame(product_rating)
      p <- ggplot(product_rating, aes(x=product_rating)) +
          geom_bar(fill=unique(product_rating$product_rating))
      p 
    
  })
  
#------------------------------------------------------------------------------#
##brand page 
#------------------------------------------------------------------------------#
  output$brand_plot <- renderPlotly({
    selected = average_rating_select2[average_rating_select2$brand == input$select_brand,]
  
    p <- ggplot(selected,
           aes(x=month, y=average.rating)) +
      geom_line() + stat_smooth()
    
    ggplotly(p, height = 400)
  })
  
  output$brand_review_analysis <- renderPlot({
    
      product = sentiment_df_brand[sentiment_df_brand$brand == input$select_brand,]
      tidy_table <- product %>% group_by(month = floor_date(review_date, unit = "month")) %>% summarise(ave_review_text_scores = sum(text_scores)/n(), ave_rating = sum(rating)/n())
      tidy_table = data.frame(tidy_table)
      p <- ggplot(tidy_table, aes(x = month))
      p <- p + geom_line(aes(y = ave_review_text_scores, colour = "Sentimental Scores"))
      p <- p + geom_line(aes(y = ave_rating/13, colour = "Ave_rating"))
      p <- p + scale_y_continuous(sec.axis = sec_axis(~.*13, name = "Average Rate stars"))
      p <- p + scale_colour_manual(values = c("blue", "red"))
      p <- p + labs(y = "Sentimental Scores",
                    x = "Month",
                    colour = "Parameter")
      p <- p + theme(legend.position = c(0.8, 0.9))
      p
  })
  
  output$pie2 <- renderPlot({
    brand_recommend <- electron_data[electron_data$brand == input$select_brand, 'reviews.doRecommend']
    brand_recommend[is.na(brand_recommend)] <- "NA"
    brand_recommend <- data.frame(brand_recommend)
    par(mar=c(0,0,0,0))
    p <- ggplot(brand_recommend, aes(x='', fill=brand_recommend)) +
    geom_bar(width = 1, stat = "count") +
    coord_polar(theta = "y", start = 0) + theme(legend.position="top",axis.title=element_blank(),axis.ticks = element_blank())
    p
  })
  
  output$bar2 <- renderPlot({
    par(mar=c(0,0,0,0))
    brand_rating <- electron_data[electron_data$brand == input$select_brand, 'reviews.rating']
    brand_rating <- brand_rating[!is.na(brand_rating)]
    brand_rating <- data.frame(brand_rating)
    p <- ggplot(brand_rating, aes(x=brand_rating)) +
        geom_bar(fill=unique(brand_rating$brand_rating))
    p
  })

  
#------------------------------------------------------------------------------#
##comparison page 
#------------------------------------------------------------------------------# 
  output$product_comparison <- renderPlotly({
    
    ggplotly(sentiment_plot_product)
  })
  
  output$brand_comparison <- renderPlotly({
    
    ggplotly(sentiment_plot_brand)
  })
    
#------------------------------------------------------------------------------#
##data page 
#------------------------------------------------------------------------------# 
  options_new <- list(columnDefs = list(list(
  targets = "_all",
  render = JS(
    "function(data, type, row, meta) {",
    "return type === 'display' && data.length > 20 ?",
    "'<span title=\"' + data + '\">' + data.substr(0, 20) + '...</span>' : data;",
    "}")
  )))
  
  output$data_table = renderDT(electron_data,
                               options = options_new, server = TRUE)
  
  
})

shinyApp(ui, server)

```

Now in order to have a deep understanding of the time span of the variable "reviews.date", we draw a jitter plot (boxplot in this case cannot show the outliers clearly) of it first. The graph below displays that most of the data range from 2014 to 2018. 


```{r}
ggplot(data=yx_select, aes(x="", y=reviews.date)) + 
  geom_jitter()

```

```{r}

ggplot(data=yx_select, aes(x=name, y=reviews.date, color=name)) + 
  geom_point(size=1.5) + theme(legend.position="none", 
                     text = element_text(size=8)) + 
  coord_flip()

```


We want to explore the rating changes of different products by time. Hence it's also important for us to preknow the distribution of reviews number for thoes elctronic prodcuts. We draw a hitogram to clearly show the count number. The diagram below shows that the product "L9HUO1UIRwCTSC-B" has most reviews. It to some extent indicates that this product may be the most popular one among all 50 electronic products.

```{r}
#yx_select$name <- abbreviate(yx_select$name, minlength = 2)
#name_count <- yx_select %>% group_by(yx_select$name) %>% summarize(count=n())

ggplot(data=yx_select, aes(x=name, fill=name)) + 
  geom_bar() + theme(legend.position="none", 
                     text = element_text(size=8)) +
  coord_flip()
```

It's worth mentioning here that the length of product names is too long, thus we use "abbreviate" function to make all the names shorter. Corresponding names are displayed below.  

```{r}
library(lubridate)
unique(yx_select$name)
```

We can now begin to explore the ratings conditioned on date for different products. Because all 50 products will make the plot too complicated, we only look one product at a time. For example, we take "L9HUO1UIRwCTSC-B". We first focus on the review number. The diagram below shows that the changes of reviews number with time. There are some variations, such as, the review number decreses nearly half from 2017 to 2018. In order to show the time changes for all products for our project, I will try to use shiny next time so that audience can choose interested products to see their corresponding graphs. 

```{r}
review_count_select <- yx_select %>% 
  group_by(name, season = floor_date(reviews.date, unit = "season")) %>% 
   summarise(n = n()) %>% mutate(freq = n/sum(n))
#'MSP4TCwFI', "L9HUO1UIRwCTSC-B", "SSXOESRRwVK", "SM", "S4CF(SLT(", "EE7AWH(" 
selected = review_count_select[
  review_count_select$name == c("L9HUO1UIRwCTSC-B" ),]
ggplot(data=selected, 
       aes(x=season, y=freq, group=name, color=name)) +
  geom_line() + stat_smooth()
```

And we can also focus on the average ratings change by time. The following diagram shows that with time goes by, the average rating of the product "L9HUO1UIRwCTSC-B" increases from 3.8 to 4.1 and then decreases to 3.6. 

```{r}
average_rating_select <- yx_select %>% 
  group_by(name, season = floor_date(reviews.date, unit = "season")) %>% 
   summarise(average.rating = mean(reviews.rating, na.rm=TRUE))
#'MSP4TCwFI', "L9HUO1UIRwCTSC-B", "SSXOESRRwVK", "SM", "S4CF(SLT(", "EE7AWH(" 
selected = average_rating_select[
  average_rating_select$name == c("L9HUO1UIRwCTSC-B"),]
ggplot(data=selected, 
       aes(x=season, y=average.rating, group=name, color=name)) +
  geom_line() + stat_smooth()
```

It seems we can not only explore the relationships from the product perspective, but also from the brand perspective. There are more than 30 kinds of brands. That's take a look for them. 

```{r}
yx_select_brand <- select(electron_data, brand, reviews.date, reviews.rating)
yx_select_brand <- yx_select_brand[rowSums(is.na(yx_select_brand)) == 0, ] #remove na rows
yx_select_brand$reviews.date <- as.Date(yx_select_brand$reviews.date)
#brand_count <- yx_select_brand %>% group_by(yx_select_brand$name) %>% summarize(count=n())
ggplot(data=yx_select_brand, aes(x=brand, fill=brand)) + 
  geom_bar() + theme(legend.position="none", 
                     text = element_text(size=8)) +
  coord_flip()
```

And we choose "Logitech" brand for example, do the same to analyse the changes with time. 

```{r}
review_count_select <- yx_select_brand %>% 
  group_by(brand, season = floor_date(reviews.date, unit = "season")) %>% 
   summarise(n = n()) %>% mutate(freq = n/sum(n))
selected = review_count_select[
  review_count_select$brand == c("Logitech"),]
ggplot(data=selected, 
       aes(x=season, y=freq, group=brand, color=brand)) +
  geom_line() + stat_smooth()
```


```{r}

average_rating_select <- yx_select_brand %>% 
  group_by(brand, season = floor_date(reviews.date, unit = "season")) %>% 
   summarise(average.rating = mean(reviews.rating, na.rm=TRUE))
selected = average_rating_select[
  average_rating_select$brand == c("Logitech"),]
ggplot(data=selected, 
       aes(x=season, y=average.rating, group=brand, color=brand)) +
  geom_line() + stat_smooth()
```

In summary:

1. We have to admit all the electronic products will be old when the new version comes to the market. This will to some extent influence the popularity of one particular product. This will result in the decrease of review number on that product. So it seems if we look at the average rating by time, it will be more unbiased. 

2. It's also interesting to compare the relationship for different brands. Why is it interesting? I think it's because most likely if customers like one particular product, they also tend to like the other products under same brand. So it's meaningful for us to compare from brand perspective. 

3. It's also worth mentioning that we cannot decide which one is popular only by the review number. For example, if one product is suck, everyone on the Internet wants to write a bad review for it, the review number will be large, however, this is not a popular product. The average rating will play an important role in this case. 

In order to make the graph more interactive, we will try to use shiny next time. Thanks.





