---
title: "Final Project of Varibale Review text Sentimental Analysis"
author: "Yunbai Zhang"
date: "11/12/2018"
output:
  html_document: default
  pdf_document: default
---

```{r echo = TRUE, fig.width = 10, fig.height = 10, warning = FALSE, cache = TRUE, include=FALSE}
library(carData)
library(cluster)
library(car)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(forcats)
library(tidyverse)
library(AER) 
library(GGally)
library(corrgram)
library(stringr)
library(extracat)
library(sentimentr)
library(plotly)

setwd('/Users/yunbaizhang/Desktop')
data = read.csv('DatafinitiElectronicsProductData.csv', header = TRUE)
## Compare review text and review title of each product by using sentimental scores. 
```


#### Compare review text and review title of each product by using sentimental scores.
##### Compare the sentimental scores of review text and the sentimental scores of review title


```{r echo = TRUE, fig.width = 15, fig.height = 10, warning = FALSE, cache = TRUE}

## The sentimental scores of review text 
my_text = get_sentences(as.character(data$reviews.text))
sen_text = sentiment_by(my_text)

## The sentimental scores of review title 
my_title = get_sentences(as.character(data$reviews.title))
sen_title = sentiment_by(my_title)

sentiment_df = data.frame(data$name, sen_text$ave_sentiment, sen_title$ave_sentiment)
colnames(sentiment_df)[1]<-"name"
colnames(sentiment_df)[2]<-"text_scores"
colnames(sentiment_df)[3]<-"title_scores"

sentiment_table <- sentiment_df %>% select(name = name, review_text_scores = text_scores,   review_title_scores = title_scores)%>% group_by(name) %>% summarise(review_text_scores = sum(review_text_scores),review_title_scores = sum(review_title_scores))

sentiment_table<- data.frame(sentiment_table)

tidy_table = sentiment_table %>% gather(`review_text_scores`,`review_title_scores`, key = 'score_type', value =scores)

theme_dotplot <- theme_bw(18) +
  theme(axis.text.y = element_text(size = rel(.4)),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = rel(.8)),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(size = 0.5),
        panel.grid.minor.x = element_blank())


ggplot(tidy_table, aes(x = scores, 
                  y = fct_reorder2(name, score_type, -scores), 
                  color = score_type)) + 
  geom_point(size = 3) + ylab("Product Name") + theme_dotplot + 
  ggtitle("Sentimental Scores for each product")

```

 * 1. Almost coinside together implies high correlation
 * 2. Logitech 915-000224 has the highest rank of review text scores and review title scores. 
 * 3. No-"super"-negative items

<br>
<br>

#### What if we compare the review text scores with reviews frequency?


```{r echo = TRUE, fig.width = 15, fig.height = 10, warning = FALSE, cache = TRUE}

my_text = get_sentences(as.character(data$reviews.text))
sen_text = sentiment_by(my_text)
sentiment_df = data.frame(data$name, sen_text$ave_sentiment)
colnames(sentiment_df)[1]<-"name"
colnames(sentiment_df)[2]<-"text_scores"


sentiment_table2 <- sentiment_df %>% select(name = name, review_text_scores = text_scores)%>% group_by(name) %>% summarise(review_text_scores = sum(review_text_scores), num_review = n())
sentiment_table2<- data.frame(sentiment_table2)

tidy_table2 = sentiment_table2 %>% gather(`review_text_scores`,`num_review`, key = 'Types', value =scores)

ggplot(tidy_table2, aes(x = scores, 
                       y = fct_reorder2(name, Types, -scores), 
                       color = Types)) + 
  geom_point() + ylab("") + theme_dotplot + xlim(0,800)+
  ggtitle("Sentimental text Scores and the number of reviews for each product")


cor(sentiment_table2$review_text_scores, sentiment_table2$num_review,  method = "pearson", use = "complete.obs")

```


* There is a pattern between number of reviews of each product and its sentimental scores. 
* Very high correlation between the number of reviews and people's feedbacks of given products.
* High-frequency of people's reviews upon some items would bring good remarks of these items.

<br>
<br>

#### What about brand instead of product name?

```{r echo = TRUE, fig.width = 8, fig.height = 8, warning = FALSE, cache = TRUE}
senti_brand = data.frame(data$brand, sen_text$ave_sentiment)
colnames(senti_brand)[1]<-"brand"
colnames(senti_brand)[2]<-"text_scores"

sentiment_table3 <- senti_brand %>% select(brand = brand, text_scores = text_scores)%>% group_by(brand) %>% summarise(text_scores = sum(text_scores))
sentiment_table3<- data.frame(sentiment_table3)

p <- ggplot(data=sentiment_table3, aes(x= reorder(brand, text_scores), y= text_scores)) +
  geom_bar(colour='blue', stat="identity") +
  guides(fill='grey')+coord_flip()

ggplotly(p)
```

* We can see that logitech was the most popular tech. Sony is on the second rank. 

<br>


#### Review's Missing value Analysis 

```{r echo = TRUE, fig.width = 8, fig.height = 8, warning = FALSE, cache = TRUE}

miss_table = colSums(is.na(data)) %>%
  sort(decreasing = FALSE)
miss_table

visna(data, sort = "c")

```

#### Which kinds of brands are more likely to have missing reviews.doRecommend or reviews.numHelpful?

<br>

#### Which kinds of product are more likely to have missing data? 

<br>

```{r echo = TRUE, fig.width = 8, fig.height = 8, warning = FALSE, cache = TRUE}

percent_missing_doRecomm <- data %>% group_by(brand) %>% 
  summarise(num_product = n(), num_na = sum(is.na(reviews.doRecommend))) %>% 
  mutate(percent_na_recommend = round(num_na/num_product, 2)) %>% 
  arrange(-percent_na_recommend)

percent_missing_doRecomm = data.frame(percent_missing_doRecomm)

p1 <- ggplot(data=percent_missing_doRecomm, aes(x= reorder(brand, percent_na_recommend), y= percent_na_recommend)) +
  geom_bar(colour='green', stat="identity") +
  guides(fill='grey')+coord_flip()+xlab('Brand')+ylab('NA Percentage')+ggtitle('Review Do Recommend Bar chart')
p1
#ggplotly(p1)
```



```{r echo = TRUE, fig.width = 10, fig.height = 10, warning = FALSE, cache = TRUE}
percent_missing_doRecomm_sub<- percent_missing_doRecomm[1:15,]
percent_missing_doRecomm_sub$brand<- droplevels(percent_missing_doRecomm_sub$brand)
ggpairs(percent_missing_doRecomm_sub, aes(color = brand))

```

* JVC has the highest percent of missing recommendation, Motorola is on the second, and Sanus is on the third. 
* Of the top 15 of the percentage of the missing recommendation, almost all the brand have similiar levels of na percentage and the percentages are between 20% and 35%  . 

<br>

#### Similar method use for reviews.numHelpful

```{r echo = TRUE, fig.width = 8, fig.height = 8, warning = FALSE, cache = TRUE}

percent_missing_doHelp <- data %>% group_by(brand) %>% 
  summarise(num_product = n(), num_na = sum(is.na(reviews.numHelpful))) %>% 
  mutate(percent_na_doHelp = round(num_na/num_product, 2)) %>% 
  arrange(-percent_na_doHelp)


p2 <- ggplot(data=percent_missing_doHelp, aes(x= reorder(brand, percent_na_doHelp), y= percent_na_doHelp)) +
  geom_bar(colour='red', stat="identity") +
  guides(fill='grey')+coord_flip()

ggplotly(p2)


```

<br>

#### What if we compare Do-Recommend and Do-Help NA data

```{r echo = TRUE, fig.width = 10, fig.height = 10, warning = FALSE, cache = TRUE}

percent_missing_doRecomm2 <- data %>% group_by(brand) %>% 
  summarise(num_product = n(), num_na = sum(is.na(reviews.doRecommend))) %>% 
  mutate(percent_na_recommend = round(num_na/num_product, 2))
percent_missing_doRecomm = data.frame(percent_missing_doRecomm2)

percent_missing_doHelp2 <- data %>% group_by(brand) %>% 
  summarise(num_product = n(), num_na = sum(is.na(reviews.numHelpful))) %>% 
  mutate(percent_na_doHelp = round(num_na/num_product, 2))

percent_missing_doHelp2 = data.frame(percent_missing_doHelp2)


compare_na = data.frame(percent_missing_doHelp2$brand, percent_missing_doHelp2$percent_na_doHelp, percent_missing_doRecomm$percent_na_recommend)


colnames(compare_na)[1]<-"brand"
colnames(compare_na)[2]<-"do_Help_na"
colnames(compare_na)[3]<-"do_Recommend_na"

cor(compare_na$do_Help_na, compare_na$do_Recommend_na)




tidy_table3 = compare_na %>% gather(`do_Help_na`,`do_Recommend_na`, key = 'Types', value =Percentage)

p3 <- ggplot(data=tidy_table3, aes(x=reorder(brand, Percentage), y=Percentage, fill=Types)) +
  geom_bar(stat="identity", position='fill')+coord_flip()+ylab('NA Percentage')+ggtitle('Review Do Recommend/Help Bar chart')
p3
#ggplotly(p3)

```

* Two variables of missing value is almost the same, except brands Lowepro and Microsoft. 





